\begin{defn*}

	If $\jpv=\tuple{X_1,\dots,X_n}$ is a vector of absolutely continuous random variables then the \ppemph{joint probability function} $f_{\jpv}$
	is a function:
	\[ f_{\jpv}\colon\bR^n\longrightarrow[0,1] \]
	Where:
	\[ \probof{\jpv\in(a_1,b_1)\times\cdots(a_n,b_n)} = \int_{a_1}^{b_1}\cdots\int_{a_n}^{b_n} f_{\jpv}(x_1,\dots,x_n)\,dx_1\cdots dx_n \]

\end{defn*}

It can be shown with relative ease using \ppref[theorem]{contProbTheorem} that if $X_1,\dots,X_n$ have a joint probability function then:
\[ \probof{X_1\leq a_1,\dots,X_n\leq a_n} = \int_{-\infty}^{a_1}\cdots\int_{-\infty}^{a_n} f_{X_1,\dots,X_n}(x_1,\dots,x_n)\,dx_n\cdots dx_1 \]

\begin{prop*}

	If $X$ and $Y$ are two absolutely continuous random variables with a joint density function, $X$ and $Y$ are independent if and only if
	$f_{X,Y}(x,y)=f_X(x)\cdot f_Y(y)$ for every real $x$ and $y$.

\end{prop*}

\begin{proof}

	If $X$ and $Y$ are independent then for every real $a$, $b$, $c$, and $d$:
	\[ \probof{X\in(a,b), Y\in(c,d)} = \probof{X\in(a,b)}\cdot\probof{Y\in(c,d)} = \int_a^b f_X(x)\,dx \cdot \int_c^d f_Y(x)\,dx = 
	\int_a^b\int_c^d f_X(x)\cdot f_Y(y)\,dy dx \]
	So $f_X(x)\cdot f_Y(y)$ satisfies the property of the joint density function, so $f_{X,Y}=f_X\cdot f_Y$.

	For the converse, we know that for every $I,J\in\borelof\bR$:
	\[ \probof{X\in I, Y\in J} = \int_I\int_J f_{X,Y}(x,y)\,dy dx = \int_I\int_J f_X(x)\cdot f_Y(y)\,dy dx =
	\int_I f_X(x)\,dx \cdot \int_J f_Y(y)\,dy = \probof{X\in I}\cdot\probof{Y\in J} \]
	So $X$ and $Y$ are independent, as required.

	\hfill$\qed$

\end{proof}

\begin{prop*}

	If $X$ and $Y$ are absoutely continuous random variables with a joint probability density function, for every real $x$:
	\[ f_X(x) = \int_{-\infty}^\infty f_{X,Y}(x,y)\,dy \]

\end{prop*}

\begin{proof}

	Remember that:
	\[ \probof{X\in(a,b)} = \probof{X\in(a,b), Y\in\bR} = \int_a^b\int_{-\infty}^\infty f_{X,Y}(x,y)\,dy dx \]
	And since this is true for every real $a$ and $b$, if we define:
	\[ f_X(x)\coloneqq\int_{-\infty}^\infty f_{X,Y}(x,y)\,dy \]
	We get that for every real $a<b$:
	\[ \probof{X\in(a,b)} = \int_a^b f_X(x)\,dx \]
	As required.

	\hfill$\qed$

\end{proof}

\begin{thrm*}

	If $X$ and $Y$ are absolutely continuous random variables with a joint probability density function, and we define $Z=X+Y$,
	we have that
	\[ f_Z(z) = \int_{-\infty}^\infty f_{X,Y}(t, z-t)\,dt \]
	is a probability density function of $Z$'s.

\end{thrm*}

\begin{proof}

	Notice that:
	\[ \probof{X\leq a, Z\leq b} = \probof{X\leq a, X+Y\leq b} \]
	So we're integrating over when $X\leq a$ and $Y\leq b-X$:
	\[ = \int_{-\infty}^a\int_{-\infty}^{b-x} f_{X,Y}(x,y)\,dy dx \]
	If we define $s=x+y$ then $dy=ds$ and $s(x,b-x)=b$ so:
	\[ = \int_{-\infty}^a\int_{-\infty}^b f_{X,Y}(x,s-x)\,ds dx \]
	If we then differentiate relative to $a$ and then $b$ we get that:
	\[ \frac{d}{db}\frac{d}{da}\probof{X\leq a, Z\leq b} = \frac{d}{db}\int_{-\infty}^b f_{X,Y}(a,s-a)\,ds = f_{X,Y}(a,b-a) \]
	But we know that this derivative is $f_{X,Z}(a,b)$, so:
	\[ f_{X,Z}(a,b) = f_{X,Y}(a,b-a) \]
	And we know that:
	\[ f_Z(z) = \int_{-\infty}^\infty f_{X,Z}(x,z)\,dx = \int_{-\infty}^\infty f_{X,Y}(x,z-x)\,dx \]
	As required.

	\hfill$\qed$

\end{proof}

\begin{defn*}

	If $X$ and $Y$ are two absolutely continuous random variables with a joint probability function, for every real $y$
	we define $\condevent{X}[Y=y]$ to have a probability density function:
	\[ f_{\condevent{X}[Y=y]} = \frac{f_{X,Y}(x,y)}{f_Y(y)} \]
	If $f_Y(y)=0$, we define this to just be $0$.

\end{defn*}

Thus we get that:
\[ \int_{-\infty}^\infty f_{\condevent X[Y=y]}(x)\cdot f_{Y}(y)\,dy = \int_{-\infty}^\infty f_{X,Y}(x,y)\,dy = f_X(x) \]
Which is the continuous version of \ppref{totProbTwoTheorem}.

Now we have arrived at the real purpose of this section, expectation.
Once again we will define expected values, but for absolutely continuous random variables.

\begin{defn*}

	If $X$ is an absolutely continuous random variable with a density function $f_X$, then its expected value is
	defined to be:
	\[ \expecof X\coloneqq\int_{-\infty}^\infty x\cdot f_X(x)\,dx \]
	If this integral converges absolutely.

	And the variance of $X$ is defined the same as before:
	\[ \varof X\coloneqq\expecof{\big(X-\expecof X\big)^2} = \expecof{X^2}-\expecof{X}^2 \]

\end{defn*}

\begin{lemm*}

	If $X$ has expectation then
	\[ \expecof X = \int_0^\infty \ccumof[X]x\,dx - \int_{-\infty}^0 \cumof[X]x \]

\end{lemm*}

\begin{proof}

	Notice that:
	\[ \int_0^\infty\ccumof[X]x\,dx = \int_0^\infty\int_x^\infty f_X(t)\,dt\,dx \]
	This is integrating over $(t,x)\in\bR^2$ where $0\leq x\leq t$ so this is equal to the integral:
	\[ = \int_0^\infty \int_0^t f_X(x)\,dx\,dt = \int_0^\infty \parens{\int_0^t\,dx}\cdot f_X(t)\,dt = \int_0^\infty t\cdot f_X(t)\,dt \]
	Similarly we see that:
	\[ \int_{-\infty}^0\cumof[X]x\,dx = -\int_{-\infty}^0 t\cdot f_X(t)\,dt \]
	And so we get that:
	\[ \int_0^\infty \ccumof[X]x\,dx - \int_{-\infty}^0 \cumof[X]x = \int_{-\infty}^\infty t\cdot f_X(t)\,dt = \expecof X \]

	\hfill$\qed$

\end{proof}


\begin{thrm*}[contlotusTheorem,The\ Law\ of\ the\ Unconscious\ Statistician]

	If $\jpv$ is a vector of absolutely continuous random variables, and $g\colon\bR^n\longrightarrow\bR$ is an integrable function such that
	$g^{-1}\big((a,b)\big)\in\borelof{\bR}^n$, then:
	\[ \expecof{g(\jpv)} = \int\!\!\cdots\!\!\int_{\bR^n}g(x_1,\dots,x_n)\cdot f_{\jpv}(x_1,\dots,x_n)\,dx_1\cdots dx_n \]

\end{thrm*}

Specificaly we have that:
\[ \expecof{g(X)} = \int_{-\infty}^\infty g(x)\cdot f_X(x)\,dx \]
I will provide a proof for this specific case.

\begin{proof}

	We know from the lemma above that:
	\[ \expecof{g(X)} = \int_0^\infty \probof{g(X)\geq x}\,dx - \int_{-\infty}^0 \probof{g(X)\leq x}\,dx \]
	Let's focus on the left integral, we know that
	\[ \int_0^\infty\probof{g(X)\geq x}\,dx = \int_0^\infty\probof{X\in g^{-1}[x,\infty)}\,dx = \int_0^\infty\int_{g^{-1}[x,\infty)}f_X(y)\,dydx \]
	This is just the integral of $f_X(y)$ over the set
	\[ A = \set{(x,y)\in\bR^2}[x\geq0, y\in g^{-1}[x,\infty)] = \set{(x,y)\in\bR^2}[0\leq x\leq g(y)] \]
	So we can swap the order of integration to get:
	\[ \int_{g^{-1}[0,\infty)}\int_0^{g(y)} f_X(y)\,dxdy = \int_{g^{-1}[0,\infty)}g(y)\cdot f_X(y)\,dy \]
	And similarly we get that:
	\[ -\int_{-\infty}\probof{g(X)\leq x}\,dx = \int_{g^{-1}[-\infty,\infty]}g(y)\cdot f_X(y)\,dy \]
	So all in all we get that:
	\[ \expecof{g(X)} = \int_{g^{-1}[0,\infty)}g(y)\cdot f_X(y)\,dy + \int_{g^{-1}[-\infty,0]}g(y)\cdot f_X(y)\,dy =
	\int_\bR g(x)\cdot f_X(x)\,dx \]
	As required.

	\hfill$\qed$

\end{proof}

\begin{thrm*}

	If $X$ is a random variable with expectation (and variance when relevant) then
	\begin{msecenumerate}
		\mitem If $X\asgeq0$ then $\expecof X\geq0$.
		\mitem $\expecof{\alpha X+\beta Y}=\alpha\expecof X+\beta\expecof Y$.
		\mitem If $X\asgeq Y$ then $\expecof X\geq\expecof Y$.
		\mitem If $X$ and $Y$ are independent $\expecof{XY}=\expecof X\cdot\expecof Y$.

		\mitem $\varof X\geq0$.
		\mitem $\varof{\alpha + X}=\varof X$ and $\varof{\alpha X}=\alpha^2\varof X$.
		\mitem If $X$ and $Y$ are independent then $\varof{X+Y}=\varof X+\varof Y$.
	\end{msecenumerate}

\end{thrm*}

\begin{proof}

	\begin{msecenumerate}[0pt]
		\mitem So we have that the integral of $f_X(x)$ over $[0,\infty)$ is $1$ and therefore $f_X(x)=0$ almost always over $(-\infty,0)$.
			Therefore:
			\[ \expecof{X} = \int_{-\infty}^\infty x\cdot f_X(x)\,dx = \int_0^\infty x\cdot f_X(x)\,dx \]
			Which is an integral of a nonnegative function and is therefore nonnegative.

		\mitem We know that by \ppref{contlotusTheorem}:
			\[ \expecof{\alpha X+\beta Y} = \iint_{\bR^2}(\alpha x+\beta y)\cdot f_{X,Y}(x,y)\,dx dy =
			\alpha\iint_{\bR^2}x\cdot f_{X,Y}(x,y)\,dx dy + \beta\iint_{\bR^2} y\cdot f_{X,Y}(x,y)\,dx dy \]
			Notice that:
			\[ \iint_{\bR^2} x\cdot f_{X,Y}(x,y)\,dx dy = \int_\bR x\cdot \int_\bR f_{X,Y}(x,y)\,dy dx = \int_\bR x\cdot f_X(x)\,dx = \expecof X \]
			And similar for $y$, so we get that this is equal to:
			\[ = \alpha\expecof X + \beta\expecof Y \]
			As required.

		\mitem Since $X\asgeq Y$, $X-Y\asgeq0$, so $\expecof{X-Y}=\expecof X-\expecof Y\geq 0$ and therefore $\expecof X\geq \expecof Y$ as required.

		\mitem Again by the law of the unconscious statistician:
			\[ \expecof{XY} = \iint_{\bR^2}xy\cdot f_{X,Y}(x,y)\,dy dx = \iint_{\bR^2}xy\cdot f_X(x)\cdot f_Y(y)\,dy dx =
			\int_\bR x\cdot f_X(x)\cdot \int_\bR y\cdot f_Y(y)\,dy dx = \]
			\[ = \int_\bR x\cdot f_X(x)\,dx \cdot \int_\bR y\cdot f_Y(y)\,dy = \expecof X\cdot\expecof Y \]

		\mitem The proofs supplied in \ppref{varTraitsTheorem} are valid here since it assumes only the traits we proved above about expectation.
	\end{msecenumerate}

	\hfill$\qed$

\end{proof}

Also note that \ppref{markovsIneqTheorem}, \ppref{chebyIneqTheorem}, \ppref{wllnTheorem}, and \ppref[theorem]{varCovRelationTheorem} also hold here since they only rely on these traits
proved above.

\begin{exam}

	If $X\sim\uniof{a,b}$ then:
	\[ \cumof[X]t = \int_a^t \frac{1}{b-a}\,dx = \frac{t-a}{b-a} \]
	If $t\in[a,b]$ and if $t>b$ then it is $1$ (since the integral is $1$), and if $t<a$ it is $0$.
	That is:
	\[ \cumof[X]t = \begin{cases} \frac{t-a}{b-a} & a\leq t\leq b \\ 1 & t>b \\ 0 & t<a \end{cases} \]
	
	And its expected value is:
	\[ \expecof X = \int_a^b x\cdot\frac1{b-a}\,dx = \frac1{b-a}\cdot\frac{x^2}2\bigg|_a^b = \frac{b^2-a^2}{2(b-a)} = \frac{a+b}2 \]

	And notice that:
	\[ \expecof{X^2} = \int_a^b x^2\cdot\frac1{b-a}\,dx = \frac1{b-a}\cdot\frac{b^3-a^3}{3} \]
	So:
	\[ \varof X = \frac{b^3-a^3}{3(b-a)} - \frac{(b-a)^2}2 = \frac{(b-a)^2}{12} \]

\end{exam}

\begin{exam}

	If $X\sim\expof\lambda$ then:
	\[ \cumof[X]t = \int_0^t \lambda\cdot e^{-\lambda x}\,dx = -e^{-\lambda x}\big|_0^t = 1 - e^{-\lambda t} \]
	For positive $t$s, and for negative $t$s it is $0$, so:
	\[ \cumof[X]t = \begin{cases} 1 - e^{-\lambda t} & t\geq0 \\ 0 & t<0 \end{cases} \]

	Its expected value is:
	\[ \expecof X = \int_0^\infty \lambda x\cdot e^{-\lambda x}\,dx = \frac{-e^{-\lambda x}(\lambda x+1)}{\lambda}\bigg|_0^\infty = \frac1\lambda \]

	And computing its variance gives $\varof X=\frac1{\lambda^2}$ (this is left as an exercise to the reader).

\end{exam}

\begin{thrm*}[expMrylsTheorem,Memorylessness\ of\ Exponential\ Distributions]

	If $X$ is an absolutely continuous random variable, $X$ distributes exponentially over $\lambda$ if and only if $\condevent{X-x_0}[X>x_0]\deq X$
	for every nonnegative real $x_0$.

\end{thrm*}

\begin{proof}

	In one direction, By definition we know that for every positive $t$:
	\[ \probof{X-x_0\geq t}[X>x_0] = \frac{\probof{X\geq t+x_0}}{\probof{X>x_0}} = \frac{\ccumof[X]{t+x_0}}{\ccumof[X]{x_0}} \]
	And we showed above that $\ccumof[X]{x}=e^{-\lambda x}$, so this is equal to:
	\[ = e^{-\lambda(t+x_0)+\lambda(x_0)} = e^{-\lambda t} \]
	And so the cummulative probability distributions are equal and therefore $\condevent{X-x_0}[X>x_0]\deq X$ as required.

	In the other direction, notice that for every nonnegative real $t$:
	\[ \probof{X\geq t} = \probof{X-x_0\geq t}[X>x_0] = \frac{\probof{X\geq t+x_0}}{\probof{X>x_0}} \]
	And since $X$ is absolutely continuous, this means:
	\[ \ccumof[X]t\cdot\ccumof[X]{x_0} = \ccumof[X]{t+x_0} \]
	Since this is true for every $x_0$, we can set $x_0=t$ and we get that $\ccumof[X]{2t}=\ccumof[X]t^2$.
	Inductively, we can show that for every $n\in\bN_1$, $\ccumof[X]{nt}=\ccumof[X]t^n$.
	Notice then that:
	\[ \ccumof[X]{t} = \ccumof[X]{n\cdot\frac1n\cdot t} = \ccumof[X]{\frac1n\cdot t}^n \]
	So $\ccumof[X]t^{\frac1n}=\ccumof[X]{\frac1n\cdot t}$.
	Now suppose that $q\in\bQ$ is a nonnegative rational, then there exists some naturals $a$ and $b$ such that $q=\frac ab$.
	So:
	\[ \ccumof[X]q = \ccumof[X]{\frac ab}=\ccumof[X]a^{\frac1b} \]
	And since $\ccumof[X]a=\ccumof[X]1^a$, this is equal to $\ccumof[X]1^{\frac ab}=\ccumof[X]1^q$.
	So if we let $\ccumof[X]1=e^{-\lambda}$ for some real $\lambda$, we get that for every rational $q$: $\ccumof[X]=e^{-\lambda q}$.
	And since the rationals are dense in $\bR$, it follows that this is true for every nonnegative real $x$.

	Since this is a complementary cumulative probability distribution, this $\lambda$ must be positive since its limit to infinity must be $0$.
	And so this is the complementary cumulative distribution of an exponential distribution at least for nonnegative $x$s.
	But it must be equal to $1$ for negative $x$s since it is decreasing and $\ccumof[X]0=1$.
	So this is exactly the complementary cumulative probability distribution of an exponential distribution over $\lambda$, so
	$\condevent{X-x_0}[X>x_0]\deq X$ as required.

	\hfill$\qed$

\end{proof}

This sheds light on an interesting connection between exponential and geometric distributions: they are both memoryless (by \ppref{geoMrylsTheorem}).
Another interesting connection is that if $X$ has an exponential distribution, then $\ceil X$ has a geometric distribution!
Let's prove this quickly.

\begin{proof}

	We know that $\probof{\ceil X=x} = \probof{X-1<X\leq x} = \cumof[X]x - \cumof[X]{x-1}$, and we can then apply the formula we found above for
	the cummulative distribution of exponential distributions above:
	\[ = 1-e^{-\lambda x} - 1 + e^{-\lambda(x-1)} = e^{-\lambda(x-1)}\big(1-e^{-\lambda}\big) \]
	So if we define $p=1-e^{-\lambda}$ we get that:
	\[ \probof{\ceil X=x} = (1-p)^{x-1}\cdot p \]
	And therefore $\ceil X\sim\geoof p=\geoof{1-e^{-\lambda}}$ as required.

	\hfill$\qed$

\end{proof}

\begin{defn*}

	An absolutely continuous random variable $X$ has a \ppemph{normal distribution} over $\mu$ and $\sigma^2$ if it has a probability density function:
	\[ f_X(t) = \frac1{\sqrt{2\pi}}\frac1\sigma\cdot e^{-\frac{(t-\mu)^2}{2\sigma^2}} \]
	This is denoted $X\sim\normof{\mu,\sigma^2}$.

\end{defn*}

The normal distribution is one of the single most important distributions in all of probability.
The reason why will become clear later on.
But first lets investigate the distribution a bit.

\begin{prop*}

	If $X\sim\normof{\mu,\sigma^2}$ then $\alpha X+\beta\sim\normof{\alpha\mu+\beta, \alpha^2\cdot\sigma^2}$

\end{prop*}

\begin{proof}

	We know that:
	\[ \probof{\alpha X+\beta\in(a,b)} = \probof{X\in\parens{\frac{a-\beta}{\alpha},\frac{b-\beta}\alpha}} =
	\int_{\frac{a-\beta}\alpha}^{\frac{b-\beta}\alpha} \frac1{\sqrt{2\pi}}\cdot\frac1\sigma\cdot e^{-\frac{(t-\mu)^2}{2\sigma^2}}\,dt \]
	(Suppose the intervals here are bidirectional, ie $(a,b)=(b,a)$ so we don't have to worry about negative $\alpha$s.)
	Let's substitute $u=\alpha t+\beta$.
	This means that $dt=\frac{du}\alpha$ so this is equal to:
	\[ = \int_a^b \frac1{\sqrt{2\pi}}\cdot\frac1{\sigma\cdot\alpha}\cdot e^{-\frac{\parens{u-(\alpha\mu+\beta)}^2}{2\sigma^2\alpha^2}}\,du \]
	So the probability density function of $\alpha X+\beta$ is exactly that of $\normof{\alpha\mu+\beta,\alpha^2\cdot\sigma^2}$, as required.

	\hfill$\qed$

\end{proof}

So then if $Z\sim\normof{0,1}$ (this is considered the ``standard'' normal distribution, or the normal normal distribution), and
$X\sim\normof{\mu,\sigma^2}$ then $X=\sigma\cdot Z+\mu$.

\begin{prop*}

	If $X\sim\normof{\mu,\sigma^2}$ then $\expecof X=\mu$ and $\varof X=\sigma^2$.

\end{prop*}

\begin{proof}

	Let's focus on the specific case of $Z\sim\normof{0,1}$.
	We know that:
	\[ \int_{-\infty}^\infty\abs t\cdot e^{-\frac{t^2}2}\,dt \leq \int_{-\infty}^\infty\abs t\cdot e^{-\abs t}\,dt \]
	Which converges, as we know.
	So $Z$ has an expected value.

	Furthermore, we know that $f_Z$ is symmetric about $0$ ($f_Z(z)=f_Z(-z)$), so $t\cdot f_Z$ is odd, and therefore its integral over $\bR$ is $0$,
	so $\expecof Z=0$.
	And as we remarked above, $X\deq\sigma Z+\mu$, so $\expecof X=\sigma\expecof Z+\mu = \mu$, as required.

	And $Z^2$ has expectation for the same reason as above, and by integration by parts:
	\[ \expecof{Z^2} = \frac1{\sqrt{2\pi}}\cdot\int_\bR t^2 e^{-\frac{t^2}2}\,dt =
	\frac1{\sqrt{2\pi}}\cdot\parens{-t e^{-\frac{t^2}2}\bigg|_{-\infty}^\infty + \int_\bR e^{-t^2}\,dt} \]
	The rightmost integral is a famous integral called the Gaussian and has a known value of $\sqrt{2\pi}$, and the left term is equal to $0$, so this is
	equal to:
	\[ = \frac1{\sqrt{2\pi}}\cdot\sqrt{2\pi} = 1 \]
	And again $X\deq\sigma Z+\mu$ so $\varof X=\sigma^2\varof Z=\sigma^2$ as required.

	\hfill$\qed$

\end{proof}

\begin{defn*}

	Due to its importance, the cumulative probability distribution of $Z\sim\normof{0,1}$ gets a special symbol:
	\[ \cumnormof{t}\coloneqq\cumof[Z]t \]

\end{defn*}

Notice that if $X\sim\normof{\mu,\sigma^2}$ then:
\[ \cumof[X]t = \probof{X\leq t} = \probof{\sigma Z+\mu\leq t} = \probof{Z\leq \frac{t-\mu}\sigma} = \cumnormof{\frac{t-\mu}\sigma} \]

